Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-21 ForegroundSimulations/ms.tex
Update figures 1, 2 and corresponding text
From 01c8a7d (master):
=====================

(*) Update figures 1 and 2

In ms.tex,

(*) Change text in accordance with updated figures

Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles. The three panels correspond to delay spectra from different positions of the point source -- 0\arcdeg (left), 45\arcdeg (middle) and 89\arcdeg (right) -- from the zenith. The phase centers are located at the source positions and hence the delay spectra are centered on $\tau = 0$~ns. The response of the simulated dish power pattern (dashed line) is comapred with that from an {\it Airy} pattern resulting from a nominal uniformly illuminated circular disk (solid line). The gray vertical lines correspond to the horizon limits at $\pm 48.7$~ns for a 14.6~m antenna spacing.

@@

At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation and thus appears as a straight vertical line centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns. As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity. They have similar magnitudes inside the horizon limits but the chromaticity of the simulated power pattern is $\sim 100$ times higher than that of an {\it Airy} pattern outside the horizon limits. In contrast, at 89\arcdeg off-axis, the two patterns have similar chromaticity in delay modes outside the horizon limits but the simulated power pattern has $\sim 100$ times more power inside the horizon limits indicating that the overall amplitude of the pattern at this location is higher relative to the nominal {\it Airy} pattern.

>>>>

Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles. The three panels correspond to delay spectra from different positions of the point source -- 0\arcdeg (left), 45\arcdeg (middle) and 89\arcdeg (right) -- from the zenith. The phase centers are located at the source positions and hence the delay spectra are centered on $\tau = 0$~ns. The response of the simulated dish power pattern (dashed line) is comapred with that from an {\it Airy} pattern resulting from a nominal uniformly illuminated circular disk (solid line). The gray vertical lines correspond to the horizon limits at $\pm 48.7$~ns for a 14.6~m antenna spacing. In all these cases, a {\it Blackman-Harris} window function has been applied along the spectral axis.

@@

At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation except that introduced by the {\it Blackman-Harris} window function and thus reproduces its Fourier response centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns. As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity. The simulated pattern not only has a higher magnitude inside the horizon limits (by a factor $\sim 10$) but also exhibits higher chromaticity (by many orders of magnitude) in modes beyond the horizon relative to that of an {\it Airy} pattern. In contrast, at 89\arcdeg off-axis, not only does the simulated pattern have higher chromaticity in high delay modes but is also two orders of magnitude higher in amplitude inside the horizon limits relative to the nominal {\it Airy} pattern.
